---
title: "dissatisfied_choropleth"
author: "Khin Htet Htet Pyone"
output: html_document
Date: 12/11/2019
---

```{r setup}
library(choroplethr)
library(choroplethrMaps)
data("country.map")
data("country.regions")

```

#Step 1:
##calculate percentage for WP132 - public satisfication on environmental perception with each country in the data set

```{r}
percentformap <- mapdata1 %>%
  dplyr::group_by(countrynew, WP132) %>%
  dplyr::summarize(N=n()) %>%
  mutate(freq=N/sum(N), pct=round((freq*100), 0))
```

#Step 2:
##filter "Dissatisfied level" from the dataset and rename the names in "countrynew" to lowercase so as to match with the country.map dataset

```{r}
dissatisfied_data <- percentformap %>% 
  filter(WP132 == "Dissatisfied") %>% 
  rename(region = countrynew,
         value = pct) %>% 
  ungroup(region) %>% 
  mutate(region = tolower(region))

```

#Step 3:
##Check the names in two dataset dissatisfied_data Vs. country.regions

```{r}
head(unique(country.map$region), 20) #from country region dataset for mapping
head(unique(dissatisfied_data$region), 20) #from disatisfied dataset
```

#Step 4:correct spacing 

```{r}
#use percentformap dataset in step 1 
percentformap$countrynew = gsub(' ', "", percentformap$countrynew)

#get disatisfied data 
dissatisfied_data <- percentformap %>% 
  filter(WP132 == "Dissatisfied") %>% 
  rename(region = countrynew,
         value = pct) %>% 
  ungroup(region) %>% 
  mutate(region = tolower(region))

country_choropleth(dissatisfied_data) #checkchoropleth mapping

```

#Step 5:check the differnt spelling for the names 

```{r}
dissatisfied_data$region[dissatisfied_data$region %in% country.regions$region] #same names  
dissatisfied_data$region[!dissatisfied_data$region %in% country.regions$region]c#different names 


```

#Step 6: recode the names 

```{r}
dissatisfied_data2 <- dissatisfied_data %>% 
  mutate(region= recode(region,
                        "burkinafaso"= "burkina faso",
                        "bosniaherzegovina"= "bosnia and herzegovina",
                        "czechrepublic"= "czech republic",
                        "costarica"= "costa rica",
                        "dominicanrepublic" = "dominican republic",
                        "elsalvador"= "el salvador",
                        "ivorycoast" = "ivory coast",
                        "newzealand"= "new zealand",
                        "southkorea"= "south korea",
                        "unitedkingdom"= "united kingdom",
                        "unitedstates"= "united states of america",
                        "srilanka"= "sri lanka",
                        "unitedarabemirates" = "united arab emirates",
                        "tanzania" = "united republic of tanzania",
                        "southafrica"= "south africa",
                        "northerncyprus"= "northern cyprus",
                        "serbia"= "republic of serbia",
                        "saudiarabia" = "saudi arabia",
                        "sierraleone" = "sierra leone",
                        "congobrazzaville"= "republic of congo"))

country_choropleth(dissatisfied_data2)
```

#Step 7: Customizing maps 
```{r}
#color
install.packages("RColorBrewer")
library(RColorBrewer)
display.brewer.all()

library(ggplot2)

country_choropleth(dissatisfied_data2,
                   num_colors = 9) +
  scale_fill_brewer (palette = "YlOrBr") +
  labs (title = "Public distisfaction on Governments' effort on Environmental Preservation by Country",
        subtitle = "Gallup 2018 data",
        fill = "Percentage of dissatisfication")

dissatisficationmap <- country_choropleth(dissatisfied_data2,
                   num_colors = 9) +
  scale_fill_brewer (palette = "YlOrBr") +
  labs (title = "Public dissatisfaction on Governments' effort for Environmental Preservation by Country",
        subtitle = "Gallup 2018 data",
        fill = "Percentage of dissatisfication",
        caption = "source: https://wpr.gallup.com")

plot(dissatisficationmap)

library(ggplot2)
#font
install.packages("extrafont")
library(extrafont)
font_import()
fonts()

 dissatisfication <- dissatisficationmap + 
  theme(text = element_text(size = 10)) + 
  theme(legend.title.align = 0.5) + 
  theme_few()
plot(dissatisfication)

```

#Step 8:save the map 
```{r}

library(ggplot2)
ggsave(dissatisfication, filename = "dissatisficationmap.png", 
       width = 20, height = 15, units = "in", dpi = 300)


#recommended format 
ggsave(dissatisfication, filename = "dissatisficationmap_5x6.png", 
       width = 5, height = 6, units = "in", dpi = 300)
```


