---
title: "Satisfied_choropleth_map"
author: "Khin Htet Htet Pyone"
Date: 12/10/2019
output: html_document
---
#Step 1: load data and requried packages 

```{r setup}
#data
gallupfilter <- read.csv(gallupfilter)
data(gallupfilter)

#packages 
library(choroplethr)
library(choroplethrMaps)
data("country.map")
data("country.regions")

```

#Step 2: Check the names of the region in country.map

```{r}
#view the first 12 region names in country.map to see the names
data("county.map", package = "choroplethrMaps" )
head(unique(country.map$region), 15)
```

#Step 3: Filter interested variables and analyze the data
##Group interested variables, summarize and calculate percentage
1. country new = A string variable lisitng each country's name and uniquely identifying each country
2.  WP 132: Efforts to preserve the environment 
(Question: In your country, are you satifsfied or disatisfied with efforts to preserve the envionment?)

```{r}

mapdata1 <- gallupfliter %>% select(countrynew, WP132)

percentformap <- mapdata1 %>%
  dplyr::group_by(countrynew, WP132) %>%
  dplyr::summarize(N=n()) %>%
  mutate(freq=N/sum(N), pct=round((freq*100), 0))

```

#Step 4: Test choropleth mapping
##filter "Satisfied" from WP132(questionresponse), rename *countrynew* to "region", ungroup region and mutate lower case so as to match with the names in the country.map data frame. 

```{r}
library(dplyr)
library(choroplethr)

plotmap1 <- percentformap %>% 
  filter(WP132 == "Satisfied") %>% 
  rename(region = countrynew,
         value = pct) %>% 
  ungroup(region) %>% 
  mutate(region = tolower(region))

```

#Step 5:Match spacing of the same in dataframe and try *choropleth mapping* 

```{r}
percentformap$countrynew = gsub(' ', "", percentformap$countrynew)

satisfied_data <- percentformap %>% 
  filter(WP132 == "Satisfied") %>% 
  rename(region = countrynew,
         value = pct) %>% 
  ungroup(region) %>% 
  mutate(region = tolower(region)) 

country_choropleth(satisfied_data)
```

#Step 6: Recode the names that are not mappable 
Some country names in my df are not the same with the *country.map* df. So, check the different names and recode. 

```{r}
#check same and different names for coding 
satisfied_data$region[satisfied_data$region %in% country.regions$region]
satisfied_data$region[!satisfied_data$region %in% country.regions$region]
country.regions$region[!country.regions$region %in% satisfied_data$region]

```

##recoding the names 
```{r}
satisfied_data2 <- satisfied_data %>% 
  mutate(region= recode(region,
                        "burkinafaso"= "burkina faso",
                        "bosniaherzegovina"= "bosnia and herzegovina",
                        "czechrepublic"= "czech republic",
                        "costarica"= "costa rica",
                        "dominicanrepublic" = "dominican republic",
                        "elsalvador"= "el salvador",
                        "ivorycoast" = "ivory coast",
                        "newzealand"= "new zealand",
                        "southkorea"= "south korea",
                        "unitedkingdom"= "united kingdom",
                        "unitedstates"= "united states of america",
                        "srilanka"= "sri lanka",
                        "unitedarabemirates" = "united arab emirates",
                        "tanzania" = "united republic of tanzania",
                        "southafrica"= "south africa",
                        "northerncyprus"= "northern cyprus",
                        "serbia"= "republic of serbia",
                        "saudiarabia" = "saudi arabia",
                        "sierraleone" = "sierra leone",
                        "congobrazzaville"= "republic of congo"))
```

#Step 7:(Optional) remove not mappable regions by row numbers 
countries (omoros, malta, mauritius, palestine, singapore) in my safisfied data set but not in *country.map* df. so, reomve them by roll number 

```{r}
#sample code: main_data2 <- main_data[ ! main_data$NAMES %in% NAMES_list, ]
#sample code: DF2 = DF1[-c(2),]
#satisfied_data3 <- satisfied_data2[!satisfied_data2$region %n%"comoros","malta", "mauritius","palestine","singapore"]

satisfied_data3 <- satisfied_data2[-c(27,80,82,100,114),]
country_choropleth(satisfied_data3)
```

#Step 8: Plotting the map 

```{r}
library(ggplot2)
satisficationmap <- country_choropleth(satisfied_data3,
                   num_colors = 9) +
  scale_fill_brewer(palette = "YlOrd") +
  labs (title = "Public Satisfaction on Governments' Effort for Environmental Preservation by country",
        subtitle = "Gallup World Poll 2018 data",
        fill = "Percentage of satisfication",
        caption = "source: https://wpr.gallup.com") 
  
library(extrafont)
library(ggthemes)

satisficationmap <- satisficationmap + theme_bw() +
  theme(text = element_text(size = 12))
  

satisficationmap
```

#Step 9: Save the map 

```{r}
library(png)
ggsave(satisficationmap, filename = "satisficationmap.png", width = 20, height = 15)

png(filename = "satisficationmap2.png",
    width = 5, height = 6,
    units = "in", res = 300)
dev.off()


ggsave(filename = "satisficationmap2.png",
       plot = fig1,device = "png",
       width = 5,height = 6,units = "in",dpi = 300)


ggsave(satisficationmap, filename = "satisficationmap2.png", 
       width = 5, height = 6, units = "in",dpi = 300
       )

```
